\tb{Place of Residence and Political Attitudes in Democracies Worldwide }

### 2018-12-11 Final Paper/PaperJLin.tex
Added some edits

Through the analysis of the Comparative Study of Electoral Systems (CSES) Module IV data, I find that place of residence does matter in influencing one's political beliefs and ideologies. More specifically, the results will allow us to draw two conclusions. First, the place of residence matters in influencing political attitudes, but this is heavily influenced on the regime's electoral formula such that if a respondent lives in a first past the post system, there is a greater pronounced difference between place of residence and ideology, but this effect is not significant in proportional representation systems. Second, the influence of place of residence on political ideology is influenced by other regime factors such as level of democracy and regime age, but there are great variations in the extent to which these forces can affect how place of residence influences political ideology.

@@

While personal factors matter to determine the development of one's morals and perceptions of political efficacy, comparative case studies on six European countries suggest that trends of globalization, along with its components of economic and social competition, can influence not only the development of a party system in a country, but also shape the viewpoints of the people in it \citep{kriesi_globalization_2006}. When party systems developed during Europian countries' transition to democracy, the people were lined on interests based on their stance on economic and social issues. As \cite{walsh_putting_2012} implies, place influences one's development of their stances on these issues, thereby leading place of residence to have the potential of influencing the survival of political parties.

@@

As a way of furthering our understanding of the way democracy is defined within the context of each country and with the model proposed by \cite{diamond2004overview}, I also include the Freedom House rating and the aggregated level of perceived corruption within each country to understand the extent of individual political freedom, equality before the law and government responsiveness. These variables both serve as added independent variables and controls but do not have hypotheses attached to them. Their inclusion is to check the Polity IV rankings and to seek to understand the relationship between the factors relating to the state of democracy in each regime.

@@

To understand where individuals see their own political values, the dependent variable reflects their self-identified ideology, a variable coded by the CSES that ranges from 0 to 10 with 0 being the most left leaning and 10 as the most right leaning ideological stance.. Since this can be rather subjective, I also created a liberalism scale that reflects individual values on government spending with a more liberal vision being those who value spending for social benefits and a more conservative view for those who do not with for such spending or for those who wish to spend more to boost defense as a means to secure their country's identity and values. (See Appendix \ref{AppendixB} for a more detailed description of this scale creation) This 9-point scale was generated from questions relating to public expenditure used in the survey. Topics for these questions include health, education, unemployment benefits, defense, old age pensions, business and industry investments, police and law enforcement and welfare benefits. Additionally, I add a value of economic equality to the measure as a means of understanding how each person values equality as part of their ideological outlook. This scale ranges from 0 to 9, with 0 being the most conservative and 9 being the most liberal. In the broadest context, respondents who score at the extreme ends of the scale are seen to be most conservative or liberal in terms of their outlook on spending, which can speak to their views on social values given their willingness to allocate government money to these groups.

@@

In the following section, I discuss the results for the regressions and comment on the observations that these regressions can suggest for the relationship between place of residence and political ideology across a sample of countries across the world.

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Worldwide}}
		\begin{tabulary}{\linewidth}{l c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Worldwide} \\
			\hline
			Small Town&.1647**  \\    
			& (..0722)   \\
			Suburban & .2714***\\ 
			& (.0934) \\
			Urban   & .2679***   \\
			& (.0721)    \\
			Constant   & 5.1086***  \\
			&(.1993) \\
			N  & 10,548  \\
			$R^2$	& 0.0454 \\
			\hline                                       
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table3}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Central/Latin America}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Mexico (2012)}&\tb{Mexico (2015)} &\tb{Peru}\\
			\hline
			Small Town  & .8064   &-1.428***    & -   \\      
			 & (1.317) & (.5255)    & -    \\
			Suburban     & -   & -   & -    \\ 
			  & -    & -   & -    \\
			Urban    & 1.107  & -1.2411***   & .2059  \\
			  &(1.1060)   & (.3994)  & (.4962)      \\
			Constant  & 12.697*** & 7.306*** & 6.820***  \\
			&(2.073)&(1.008)&(1.390) \\
			N   &96   & 327 & 267   \\
			$R^2$ & 0.2811   &0.0695   &0.0557     \\
			\hline                   
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table4}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Western Europe}}
		\begin{tabulary}{\linewidth}{l c c }
			\\
			\hline
			\tb{Place of Residence}&\tb{Germany}&\tb{France} \\
			\hline
			Small Town   & -.0753 &-.1266  \\      
			& (.2080)  & (.1680)   \\
			Suburban   & .2526 & -.0432    \\ 
			 & (.3290)  & (.2310)    \\
			Urban   & -.2544 & -.6460***    \\
			 &(.2490)  & (.1706)   \\
			Constant  & 5.399***  & 1.3237** \\
			&(0.0845)&(.6009) \\
			N  &427  & 1,332    \\
			$R^2$  &0.1072 &0.0866  \\
			\hline                                       
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table5}
\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Central Europe}}
		\begin{tabulary}{\linewidth}{l c c c c}
			\\
			\hline
			\tb{Place of Residence} &\tb{Austria}&\tb{Czech Republic}& \tb{Poland} &\tb{Slovakia} \\
			\hline
			Small Town&.6270**& -.1272 & .3032 & .3954  \\
			&(.3139) & (.2920) & (.2002) & (.3216) \\
			Suburban&-.0326& -.4467&.0666 & 2.1723\\
			&(.3343)&(.4993) & (.3104) & (.1.107)\\
			Urban&.3822&.5199 & .0954 & 1.1440 \\
			&(.3888) &(.2944) & (.2662) & (.4518) \\
			Constant& 4.014***& 3.930***& 5.096*** & 4.3473***  \\
			&(.9272) & (.8696) & (.8646) & (1.127) \\
			N&247& 511& 895 & 392 \\
			$R^2$&0.1126&0.2538 & 0.1348 & 0.1498 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table6}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Scandinavia}}
		\begin{tabulary}{\linewidth}{l c c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Finland}&\tb{Iceland}&\tb{Sweden} \\
			\hline
			Small Town&.2546&1.131***&-.0247 \\
			&(.4143)&(.4036)&(.4636) \\
			Suburban&.0600&1.866***&.0325 \\
			&(.3463)&(.4081)&(.4431) \\
			Urban&-.6608&.9035**& .0217\\
			&(.4514)&(.3993)&(.4006) \\
			Constant&6.5998***&6.063***&2.352** \\
			&(1.123)&(.8182)&(1.116) \\
			N&187&428&330\\
			$R^2$&0.2158&0.1688&0.0677 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table7}
	\end{table}
\end{singlespace}

@@

\begin{landscape}
	\begin{table}
		\centering
		\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Southwestern Europe}}
		\begin{tabulary}{\linewidth}{l c c c c c c}
			\\
			\hline
			\tb{Residence}& \tb{Bulgaria}& \tb{Greece ('12)}& \tb{Greece ('15)} & \tb{Montenegro} & \tb{Romania ('12)} & \tb {Romania ('14)}\\
			\hline
			Small Town&.2627 &-.0542 &-.3076 & -1.3042** & .0309 & .0511\\
			&(.3319)& (.5039) & (.4971) & (.5882) & (.3619) & (.6030)\\
			Suburban& .3400 & -.8706 &-.3540 & -.2289  &.2880 &.7052\\
			& (.2941) &(.4878) & (.5298) & (.8432) & (.8747) & (.7604)\\
			Urban& -.2833& -.8586** & -.3762 & .1149& 1.1965** & -.9908\\
			& (.4204)& (.3852) & (.4642) & (1.1020) & (.3769) & (.8057)\\
			Constant& 11.310*** &3.7549*** & 2.2395*** &7.633*** & 5.1379*** & 6.262***\\
			& (.9980) & (1.2241)  & (.9403) & (2.1586)& (1.3297) & (2.300)\\
			N& 440 & 360 & 476 & 152 & 566 &245\\
			$R^2$&0.5188 &0.1740& 0.1346 &0.1939& 0.0313 &0.1064 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table8}
	\end{table}
\end{landscape}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Eastern Europe}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence} & \tb{Latvia (2011)} &\tb{Latvia (2014)} \\
			\hline
			Small Town &.0423 &-.1924 \\
			&(.5399) & (.4346) \\
			Suburban&- & -.1413 \\
			& - & (.5755) \\
			Urban&-.3829&-.3400 \\
			& (.4270) & (.3978) \\
			Constant & 5.502*** &7.8918*** \\
			& (1.4972) & (1.146) \\
			N&188 & 276\\
			$R^2$& 0.1469 &0.0424 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table9}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Middle East}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence}&\tb{Israel} & \tb{Turkey} \\
			\hline
			Small Town&.5796 & .4447 \\
			&(.3041)  & (.6314)\\
			Suburban&.5968 &.3318 \\
			& (.3478)  & (.6740)\\
			Urban &- & .4440\\
			&- & (.5626)\\
			Constant& 6.1311*** &1.953 \\
			& (.9217)  & (1.813)\\
			N&439 & 251\\
			$R^2$&0.2978 & 0.1484 \\
			\hline 
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table10}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Africa}}
		\begin{tabulary}{\linewidth}{l c}
			\\
			\hline
			\tb{Place of Residence}& \tb{South Africa} \\
			\hline
			Urban&-1.0519** \\
			&(.4499)\\
			Constant&8.7909*** \\
			& (1.5955) \\
			N& 220\\
			$R^2$&0.0660 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table11}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering 
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Asia}}
		\begin{tabulary}{\linewidth}{l c c}
			\\
			\hline
			\tb{Place of Residence} & \tb{Japan} & \tb{South Korea}\\
			\hline
			Small Town &.6578** & -.5849 \\
			&(.2648) & (.4634)\\
			Suburban&.5867** & -2.233*** \\
			& (.2796) & (.7757)\\
			Urban & .6344** &.0059 \\
			& (.2576) & (4217)\\
			Constant& 6.0168*** & .4540 \\
			& (.7272) & (1.495)\\
			N&528 & 267\\
			$R^2$&0.0886 & 0.2113\\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table12}
	\end{table}
\end{singlespace}

@@

Regionally speaking, the Philippines are often considered to be part of Asia given the ethnic identities of the people, however, their geographic location can also qualify them to be a pacific island. Therefore, while Table \ref{table13} shows the trends of the Philippines and New Zealand, I will analyze them in the broader context of Asia. The Philippines is a relatively young democracy and has a rating of 8 on the level of democracy scale. New Zealand has one of the most free in the region (similar to Japan) and is also the oldest. Yet, none of these two countries show a place divide when it comes to political ideology. Therefore, in Asia as a whole, the presence of a rural-urban divide in some countries and not others suggest that there is not a regional influence not are there patterns between levels of democracy, regime age, and electoral formula that influence the relationship between place of residence and political ideology.

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Pacific Islands}}
		\begin{tabulary}{\linewidth}{l c c }
			\\
			\hline
			\tb{Place of Residence}&\tb{New Zealand (2011)}&\tb{Philippines}\\
			\hline
			Small Town & -.3603  & .6010  \\      
			& (.3050) & (.8141)    \\
			Suburban  & -   & .7878  \\ 
			 & -   & (1.4391)       \\
			Urban  & -.0154   & .3447 \\
			 &(.2926)   & (.4770)      \\
			Constant  & 5.176***  & 7.838***   \\
			&(.8503)&(1.8952) \\
			N  &586 & 115  \\
			$R^2$  &0.0491  &0.0627     \\
			\hline                                       
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table13}
	\end{table}
\end{singlespace}

@@

%Fixed to include Controls
\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Issue Stances - General Trends}}
	\begin{tabulary}{\linewidth}{l c}
		\\
		\hline
		\tb{Place of Residence} & \tb{Worldwide} \\
		\hline 
		Small Town&.0432 \\
		&(.0278)\\
		Suburban&.0082\\
		&(.0352) \\
		Urban&.0995*** \\
		&(.0272)\\
		Constant&2.7915*** \\
		&(.0762) \\
		N&9.662 \\
		$R^2$&0.0195 \\
		\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table14}
\end{table}

@@

In Southwestern Europe, Greece confirms the \e{Issue Stances} hypothesis such that the urban residents are more likely than chance to say that they are more open to government spending than rural residents. This pattern is observed in the oppesite direction for Montenegro and Romania in 2012. Yet, the same cannot be said for Latvia, the sole case here from Eastern Europe.

@@

Table \ref{table15} shows the influence of each of the macro variables, when taken together, on the relationship between place of residence and individual placement on political ideology and on the objective measures seen in the liberalism measure.

@@

In the next sections, I run interactions with each of the macro variables listed under Hypothesis 3 along with the  Freedom House Ratings and Corruption Perception Index as independent and control variables to see how these factors influence the relationship of place and ideology.

@@

\section{\e{Self-Identified Ideology} - General Trends}
\label{AppendixD}

>>>>

Through the analysis of the Comparative Study of Electoral Systems (CSES) Module IV data, I find that place of residence does matter in influencing one's political beliefs and ideologies. More specifically, the results will allow us to draw a key conclusion: The place of residence matters in influencing political attitudes, but this is heavily influenced by regime factors such as level of democracy, regime age electoral formula, Freedom House Rating and corruption.

@@

While personal factors matter to determine the development of one's morals and perceptions of political efficacy, comparative case studies on six European countries suggest that trends of globalization, along with its components of economic and social competition, can influence not only the development of a party system in a country, but also shape the viewpoints of the people in it \citep{kriesi_globalization_2006}. When party systems developed during European countries' transition to democracy, the people were lined on interests based on their stance on economic and social issues. As \cite{walsh_putting_2012} implies, place influences one's development of their stances on these issues, thereby leading place of residence to have the potential of influencing the survival of political parties.

@@

As a way of furthering our understanding of the way democracy is defined within the context of each country and with the model proposed by \cite{diamond2004overview}, I also include the Freedom House Rating and the aggregated level of perceived corruption within each country to understand the extent of individual political freedom, equality before the law and government responsiveness. These variables both serve as added independent variables and controls but do not have hypotheses attached to them. Their inclusion is to check the Polity IV rankings and to seek to understand the relationship between the factors relating to the state of democracy in each regime.

@@

To understand where individuals see their own political values, the dependent variable reflects their self-identified ideology, a variable coded by the CSES that ranges from 0 to 10 with 0 being the most left leaning and 10 as the most right leaning ideological stance.. Since this can be rather subjective, I also created a liberalism scale that reflects individual values on government spending with a more liberal vision being those who value spending for social benefits and a more conservative view for those who do not with for such spending or for those who wish to spend more to boost defense as a means to secure their country's identity and values. (See Appendix \ref{AppendixB} for a more detailed description of this scale creation) This 9-point scale was generated from questions relating to public expenditure used in the survey. Topics for these questions include health, education, unemployment benefits, defense, old age pensions, business and industry investments, police and law enforcement and welfare benefits. Additionally, I add a value of economic equality to the measure as a means of understanding how each person values equality as part of their ideological outlook. This scale ranges from 0 to 9, with 9 being the most conservative and 0 being the most liberal. In the broadest context, respondents who score at the extreme ends of the scale are seen to be most conservative or liberal in terms of their outlook on spending, which can speak to their views on social values given their willingness to allocate government money to these groups.

@@

In the following section, I discuss the results for the regressions and comment on the observations that these regressions can suggest for the relationship between place of residence and political ideology across a sample of countries across the world. The discussion of countries will be broken down by general geographic region in order to understand if and how neighborhood differences influence these trends as they usually do with it comes to a country's transition to democracy \citep{brinks2006diffusion}.

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Worldwide}}
		\begin{tabulary}{\linewidth}{l c}
			\hline
			\tb{Place of Residence}&\tb{Worldwide} \\
			\hline
			Small Town&.1647**  \\    
			& (..0722)   \\
			Suburban & .2714***\\ 
			& (.0934) \\
			Urban   & .2679***   \\
			& (.0721)    \\
			Constant   & 5.1086***  \\
			&(.1993) \\
			N  & 10,548  \\
			$R^2$	& 0.0454 \\
			\hline                                       
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table3}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Central/Latin America}}
		\begin{tabulary}{\linewidth}{l c c c}
			\hline
			\tb{Place of Residence}&\tb{Mexico (2012)}&\tb{Mexico (2015)} &\tb{Peru}\\
			\hline
			Small Town  & .8064   &-1.428***    & -   \\      
			 & (1.317) & (.5255)    & -    \\
			Suburban     & -   & -   & -    \\ 
			  & -    & -   & -    \\
			Urban    & 1.107  & -1.2411***   & .2059  \\
			  &(1.1060)   & (.3994)  & (.4962)      \\
			Constant  & 12.697*** & 7.306*** & 6.820***  \\
			&(2.073)&(1.008)&(1.390) \\
			N   &96   & 327 & 267   \\
			$R^2$ & 0.2811   &0.0695   &0.0557     \\
			\hline                   
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table4}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Western Europe}}
		\begin{tabulary}{\linewidth}{l c c }

			\hline
			\tb{Place of Residence}&\tb{Germany}&\tb{France} \\
			\hline
			Small Town   & -.0753 &-.1266  \\      
			& (.2080)  & (.1680)   \\
			Suburban   & .2526 & -.0432    \\ 
			 & (.3290)  & (.2310)    \\
			Urban   & -.2544 & -.6460***    \\
			 &(.2490)  & (.1706)   \\
			Constant  & 5.399***  & 1.3237** \\
			&(0.0845)&(.6009) \\
			N  &427  & 1,332    \\
			$R^2$  &0.1072 &0.0866  \\
			\hline                                       
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table5}
\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Central Europe}}
		\begin{tabulary}{\linewidth}{l c c c c}

			\hline
			\tb{Place of Residence} &\tb{Austria}&\tb{Czech Republic}& \tb{Poland} &\tb{Slovakia} \\
			\hline
			Small Town&.6270**& -.1272 & .3032 & .3954  \\
			&(.3139) & (.2920) & (.2002) & (.3216) \\
			Suburban&-.0326& -.4467&.0666 & 2.1723\\
			&(.3343)&(.4993) & (.3104) & (.1.107)\\
			Urban&.3822&.5199 & .0954 & 1.1440 \\
			&(.3888) &(.2944) & (.2662) & (.4518) \\
			Constant& 4.014***& 3.930***& 5.096*** & 4.3473***  \\
			&(.9272) & (.8696) & (.8646) & (1.127) \\
			N&247& 511& 895 & 392 \\
			$R^2$&0.1126&0.2538 & 0.1348 & 0.1498 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table6}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Scandinavia}}
		\begin{tabulary}{\linewidth}{l c c c}

			\hline
			\tb{Place of Residence}&\tb{Finland}&\tb{Iceland}&\tb{Sweden} \\
			\hline
			Small Town&.2546&1.131***&-.0247 \\
			&(.4143)&(.4036)&(.4636) \\
			Suburban&.0600&1.866***&.0325 \\
			&(.3463)&(.4081)&(.4431) \\
			Urban&-.6608&.9035**& .0217\\
			&(.4514)&(.3993)&(.4006) \\
			Constant&6.5998***&6.063***&2.352** \\
			&(1.123)&(.8182)&(1.116) \\
			N&187&428&330\\
			$R^2$&0.2158&0.1688&0.0677 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table7}
	\end{table}
\end{singlespace}

@@

\begin{landscape}
	\begin{table}
		\centering
		\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Southwestern Europe}}
		\begin{tabulary}{\linewidth}{l c c c c c c}

			\hline
			\tb{Residence}& \tb{Bulgaria}& \tb{Greece ('12)}& \tb{Greece ('15)} & \tb{Montenegro} & \tb{Romania ('12)} & \tb {Romania ('14)}\\
			\hline
			Small Town&.2627 &-.0542 &-.3076 & -1.3042** & .0309 & .0511\\
			&(.3319)& (.5039) & (.4971) & (.5882) & (.3619) & (.6030)\\
			Suburban& .3400 & -.8706 &-.3540 & -.2289  &.2880 &.7052\\
			& (.2941) &(.4878) & (.5298) & (.8432) & (.8747) & (.7604)\\
			Urban& -.2833& -.8586** & -.3762 & .1149& 1.1965** & -.9908\\
			& (.4204)& (.3852) & (.4642) & (1.1020) & (.3769) & (.8057)\\
			Constant& 11.310*** &3.7549*** & 2.2395*** &7.633*** & 5.1379*** & 6.262***\\
			& (.9980) & (1.2241)  & (.9403) & (2.1586)& (1.3297) & (2.300)\\
			N& 440 & 360 & 476 & 152 & 566 &245\\
			$R^2$&0.5188 &0.1740& 0.1346 &0.1939& 0.0313 &0.1064 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table8}
	\end{table}
\end{landscape}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Eastern Europe}}
		\begin{tabulary}{\linewidth}{l c c}

			\hline
			\tb{Place of Residence} & \tb{Latvia (2011)} &\tb{Latvia (2014)} \\
			\hline
			Small Town &.0423 &-.1924 \\
			&(.5399) & (.4346) \\
			Suburban&- & -.1413 \\
			& - & (.5755) \\
			Urban&-.3829&-.3400 \\
			& (.4270) & (.3978) \\
			Constant & 5.502*** &7.8918*** \\
			& (1.4972) & (1.146) \\
			N&188 & 276\\
			$R^2$& 0.1469 &0.0424 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table9}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Middle East}}
		\begin{tabulary}{\linewidth}{l c c}

			\hline
			\tb{Place of Residence}&\tb{Israel} & \tb{Turkey} \\
			\hline
			Small Town&.5796 & .4447 \\
			&(.3041)  & (.6314)\\
			Suburban&.5968 &.3318 \\
			& (.3478)  & (.6740)\\
			Urban &- & .4440\\
			&- & (.5626)\\
			Constant& 6.1311*** &1.953 \\
			& (.9217)  & (1.813)\\
			N&439 & 251\\
			$R^2$&0.2978 & 0.1484 \\
			\hline 
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table10}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Africa}}
		\begin{tabulary}{\linewidth}{l c}

			\hline
			\tb{Place of Residence}& \tb{South Africa} \\
			\hline
			Urban&-1.0519** \\
			&(.4499)\\
			Constant&8.7909*** \\
			& (1.5955) \\
			N& 220\\
			$R^2$&0.0660 \\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table11}
	\end{table}
\end{singlespace}

@@

\begin{singlespace}
	\begin{table}[H]
		\centering 
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Asia}}
		\begin{tabulary}{\linewidth}{l c c}

			\hline
			\tb{Place of Residence} & \tb{Japan} & \tb{South Korea}\\
			\hline
			Small Town &.6578** & -.5849 \\
			&(.2648) & (.4634)\\
			Suburban&.5867** & -2.233*** \\
			& (.2796) & (.7757)\\
			Urban & .6344** &.0059 \\
			& (.2576) & (4217)\\
			Constant& 6.0168*** & .4540 \\
			& (.7272) & (1.495)\\
			N&528 & 267\\
			$R^2$&0.0886 & 0.2113\\
			\hline
		\end{tabulary}
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table12}
	\end{table}
\end{singlespace}

@@

By geography, the Philippines are often considered to be part of Asia given the ethnic identities of the people; however, their geographic location can also qualify them to be a pacific island. Therefore, while Table \ref{table13} shows the trends of the Philippines and New Zealand, I will analyze them in the broader context of Asia. The Philippines is a relatively young democracy and has a rating of 8 on the level of democracy scale. New Zealand has one of the most free in the region (similar to Japan) and is also the oldest. Yet, none of these two countries show a place divide when it comes to political ideology. Therefore, in Asia as a whole, the presence of a rural-urban divide in some countries and not others suggest that there is not a regional influence not are there patterns between levels of democracy, regime age, and electoral formula that influence the relationship between place of residence and political ideology.

\begin{singlespace}
	\begin{table}[H]
		\centering
		%\def\arraystretch{1.5}
		\caption{\tb{Self-Placement Ideology - Pacific Islands}}
		\begin{tabulary}{\linewidth}{l c c }

			\hline
			\tb{Place of Residence}&\tb{New Zealand (2011)}&\tb{Philippines}\\
			\hline
			Small Town & -.3603  & .6010  \\      
			& (.3050) & (.8141)    \\
			Suburban  & -   & .7878  \\ 
			 & -   & (1.4391)       \\
			Urban  & -.0154   & .3447 \\
			 &(.2926)   & (.4770)      \\
			Constant  & 5.176***  & 7.838***   \\
			&(.8503)&(1.8952) \\
			N  &586 & 115  \\
			$R^2$  &0.0491  &0.0627     \\
			\hline                                       
		\end{tabulary} 
		\\
		\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
		\e{Reference:} A rural place of residence serves as the baseline for comparison
		\label{table13}
	\end{table}
\end{singlespace}

@@

%Fixed to include Controls
\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{Issue Stances - General Trends}}
	\begin{tabulary}{\linewidth}{l c}

		\hline
		\tb{Place of Residence} & \tb{Worldwide} \\
		\hline 
		Small Town&.0432 \\
		&(.0278)\\
		Suburban&.0082\\
		&(.0352) \\
		Urban&.0995*** \\
		&(.0272)\\
		Constant&2.7915*** \\
		&(.0762) \\
		N&9.662 \\
		$R^2$&0.0195 \\
		\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table14}
\end{table}

@@

In Southwestern Europe, Greece confirms the \e{Issue Stances} hypothesis such that the urban residents are more likely than chance to say that they are more open to government spending than rural residents. This pattern is observed in the oppesite direction for Montenegro and Romania in 2012. Yet, the same cannot be said for Latvia in their 2014 election, the sole case here from Eastern Europe.

@@

Table \ref{table15} shows the influence of each of the macro variables, when taken together, on the relationship between place of residence and individual placement on political ideology and on the objective measures seen in the liberalism scale.

@@

In the next sections, I run interactions with each of the macro variables listed under Hypothesis 3 along with the  Freedom House Ratings and Corruption Perception Index as independent and control variables to see how these factors influence the relationship of place and ideology. Appendix \ref{Online} contains the technical processes that were behind these calculations.

@@

\section{Dependent Variables -- General Trends}
\label{AppendixD}
